Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex

\begin{figure*}[t]
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}\label{f:cartpole}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}\label{f:mountaincar}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
    \caption{}\label{f:maze_results}
  \end{subfigure}
  \caption{(a) transfer from $10$ sources in Cartpole, (b) transfer from $10$ source tasks in Mountain Car, and (c) transfer from $10$ sources in Maze \ref{fig:maze6}---see App. \ref{}.}
  \label{fig:ccmazeplots}
\end{figure*}

For this setting we propose a maze environment, such as those in Fig. \ref{}, for a robotic agent to navigate. We created a set of 20 mazes---see App \ref{}---of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze. In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}). Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measurements to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision of $9$ equally-spaced directions in $[-90,90º]$ relative to its orientation. In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike. Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation. Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.

The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience. Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.

The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm. Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13. As before, $20$ independent runs with randomized sources to transfer are averaged and shown in Fig. \ref{}, in this case $5$ source tasks were used for each trial. While these mazes pose a challenge for our algorithm, we can see that 1-MGVT is capable to still capture useful information from the sources and adapt to the target mazes which is demonstrated by the increased slope in the learning curve. \todo{actually, decide how to improve these results}

>>>>

\begin{figure*}[t]
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}\label{f:cartpole}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}\label{f:mountaincar}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
    \caption{}\label{f:maze_results}
  \end{subfigure}
  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
  \label{fig:ccmazeplots}
\end{figure*}

In our last experiment, we consider a robotic agent navigating mazes. At the beginning of each episode, the agent is dropped to a random position in a $10m^2$ maze and must reach a goal area in the smallest time possible. The robot is equipped with sensors detecting its absolute position, its orientation, the distance to any obstacle within $2m$ in $9$ equally-spaced directions, and whether the goal is detected in the same range. The only actions available are \textit{move forward} with speed $0.5m/s$ or \textit{rotate} (in either direction) with speed of $\pi/8 rad/s$. Each time step corresponds to $1s$ of simulation. The reward is $1$ for reaching the goal and $0$ otherwise, while the discount factor is $\gamma=0.99$. For this experiment, we design a set of $20$ different mazes and solve them using a DDQN with two layers of $32$ neurons and ReLU activations. Then, we fix a target maze and transfer from $5$ source mazes uniformly sampled from such set (excluding the chosen target). To further asses the robustness of our method, we now consider transferring from the $Q$-functions learned by DDQNs instead of those obtained by minimizing the TD error as in the previous domains. From our considerations of Sec. \ref{sec:td} and \ref{sec:theory}, the fixed-points of the two algorithms are different, which creates a further challenge for our method. We show the results for a fixed target maze in Fig. \ref{}, while referring the reader to App.  \ref{} for the illustration of our mazes and additional results. Once again, MGVT achieves a remarkable speed-up over (no-transfer) DDQN. This time, using $3$ components achieves slightly better performance than using only $1$, which is likely due to the fact that the task distribution is much more complicated than in the previous domains. For the same reason, GVT shows negative transfer and performs even worse than no-transfer.

%For this setting we propose a maze environment, such as those in Fig. \ref{}, for a robotic agent to navigate. We created a set of 20 mazes---see App \ref{}---of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze. In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}). Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measurements to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision of $9$ equally-spaced directions in $[-90,90º]$ relative to its orientation. In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike. Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation. Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.

%The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience. Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.

%The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm. Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13. As before, $20$ independent runs with randomized sources to transfer are averaged and shown in Fig. \ref{}, in this case $5$ source tasks were used for each trial. While these mazes pose a challenge for our algorithm, we can see that 1-MGVT is capable to still capture useful information from the sources and adapt to the target mazes which is demonstrated by the increased slope in the learning curve. \todo{actually, decide how to improve these results}
